### 2016-12-31 2017mergingmerges/section/XX-Processes.tex
rough shape of evaluation rules

>>>>

\begin{figure}

$$
\arrLR{
  \boxed{\ProcInject{\Proc}{\Chan}{\Value}{\Proc}}
}{
  \boxed{\ProcsInject{\sgl{\Proc}}{\Chan}{\Value}{\sgl{\Proc}}}
}
$$

$$
\ruleIN{
  c=@none@ \in @ins@~p
}{
  \ProcInject{p}{c}{v}{p ~@ins@~ \{ c = @pending@~v\}}
}{InjectValue}
\ruleIN{
  c \not\in @ins@~p
}{
  \ProcInject{p}{c}{v}{p}
}{InjectIgnore}
$$

$$
\ruleIN{
  \forall i.~ \ProcInject{p_i}{c}{v}{p'_i}
}{
  \ProcsInject{\sgl{p_i}}{c}{v}{\sgl{p'_i}}
}{ProcessesInject}
$$

\caption{Process evaluation: inject}
\label{fig:Process:Eval:Inject}
\end{figure}

\begin{figure}

$$
\alpha~@:=@~ \Push~\Chan~\Value ~|~ \tau
$$

$$
@let@~@block@~p~=~@blocks@~p~(@label@~p)
$$

$$
\arrLR{
  \boxed{\ProcShake{\Proc}{\alpha}{\Proc}}
}{
  \boxed{\ProcsShake{\sgl{\Proc}}{\alpha}{\sgl{\Proc}}}
}
$$

\TODO{These could be split into smaller judgment forms with something like @block;ins;sigma => label;ins;sigma;alpha@}

\TODO{Missing the update heap on output. Should be @pull c x l[u] => p heap[u]@}

$$
\ruleIN{
  c=@pending@~v \in @ins@~p
  \quad
  @pull@~c~x~l'~=~@block@~p
}{
  \ProcShake{p}{\tau}{p ~@ins@~ \{ c = @have@\},~@label@~=~l', @heap@ \{ x = v\}}
}{Pull}
\ruleIN{
  c=@have@ \in @ins@~p
  \quad
  @drop@~c~l'~=~@block@~p
}{
  \ProcShake{p}{\tau}{p ~@ins@~ \{ c = @none@\},~@label@~=~l'}
}{Drop}
$$

$$
\ruleIN{
  @push@~c~e~l'~=~@block@~p
}{
  \ProcShake{p}{\Push~c~(e~(@heap@~p))}{p~@label@~=~l'}
}{Push}
\ruleIN{
  @jump@~l'~=~@block@~p
}{
  \ProcShake{p}{\tau}{p~@label@~=~l'}
}{Jump}
$$

$$
\ruleIN{
  @case@~e~l_t~l_f~=~@block@~p
  \quad
  e~(@heap@~p)~=~@t@
}{
  \ProcShake{p}{\tau}{p~@label@~=~l_t}
}{CaseT}
\ruleIN{
  @case@~e~l_t~l_f~=~@block@~p
  \quad
  e~(@heap@~p)~=~@f@
}{
  \ProcShake{p}{\tau}{p~@label@~=~l_f}
}{CaseF}
$$

$$
\ruleIN{
  \ProcShake{p_i}{\tau}{p'_i}
}{
  \ProcsShake{
    \sgl{p_0 \ldots p_i \ldots p_n}
  }{\tau}{
    \sgl{p_0 \ldots p'_i \ldots p_n}
  }
}{ProcessesInternal}
$$

$$
\ruleIN{
  \ProcShake{p_i}{\Push~c~v}{p'_i}
  \quad
  \forall j~|~j \neq i.~
  \ProcInject{p_j}{c}{v}{p'_j}
}{
  \ProcsShake{
    \sgl{p_0 \ldots p_i \ldots p_n}
  }{\Push~c~v}{
    \sgl{p'_0 \ldots p'_i \ldots p'_n}
  }
}{ProcessesPush}
$$

\caption{Process evaluation: shake}
\label{fig:Process:Eval:Shake}
\end{figure}

We use the ``inject and shake'' method of evaluation. (This isn't a real thing.)

Rules in figure~\ref{fig:Process:Eval:Inject} are about injecting values into a process; these are the values used when the process performs a @pull@.
The injected values may be pushed values from other processes for internal streams, or may come from an external source for the overall nest's input streams.
For the map/map example, the values for @xs@ would be injected externally, but the values for @ys@ will be injected into the second process from the first process.
Injection is just about orchestrating values between processes, and no actual computation happens here; it just makes values available to be pulled.

The rules in figure~\ref{fig:Process:Eval:Shake} are the `shake' part of evaluation, where actual computation occurs. 
As usual, $\alpha$ denotes the message type, with $\tau$ being an internal message. The \Push~ message is a single value being output on a channel.
